### 2019-04-17 paper/template/conference_041818.tex
Start write the pepa

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Complete Workload Analysis of Real Autonomous Driving System: Apollo, Baidu Inc.}

\author{\IEEEauthorblockN{1\textsuperscript{st} Alessandro Toschi}
\IEEEauthorblockA{\textit{Shanghai Jiao Tong University} \\
\textit{}
Shanghai, China \\
aleto\_95@sjtu.edu.cn}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Jingwen Leng}
\IEEEauthorblockA{\textit{Shanghai Jiao Tong University} \\
\textit{}
Shanghai, China \\
leng-jw@sjtu.edu.cn}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
}
\maketitle

\begin{abstract}
    Autonomous driving is a field that gathers many interest from the academics world and from industry leaders.\\
    The software of an autonomous driving systems (ADS) incorporates the state-of-the-art from many disciplines, such as computer vision, robotics, geolocalization.
    Although the high level architecture of an autonomous driving system and the main algorithms used are known, the complete analysis of a real ADS is still difficult, especially for what concerns the modules interdependencies, interactions, either software and hardware, and pre- and post-processing.\\
    In this paper, we want to extract those point of views and quantify them according different architectural aspects: response times, memory movements, complexity and CPU-GPU relationship.\\
    The analysis is based on the open-source Apollo ADS developed by Baidu and is focused on the most important modules: perception, prediction and planning.
\end{abstract}

\section{Introduction}
Autonomous driving system has several design constraints \cite{b1} to be met in order to produce a safe and reliable output.

Response time \cite{b1} is crucial for the predictability and accuracy of the system, especially when multiple sensor and components are present, each of them with a processing routine associated.
The maximum response time, that has been adopted as standard in the field of autonomous driving, is 100 ms and should ensure a proper and safe reaction to any possible situation.
Several processing routines use time deltas to perform corrections and projections of input and if those time-deltas are exceeding context-related thresholds then the input is discarded, losing some potential useful information, so limiting the response time will affect also the accuracy of the system.

Autonomous driving requirements.\\
Introduction to Apollo: what is it, how is it implemented, data communication.\\
Modules that are going to be analyzed.\\
Image of apollo software architecture.\\

\section{Perception}
Perception diagram.
General description: what it does, sensors descriptions, output and general overview.

For each component: camera, lidar segmentation, lidar recognition, fusion component and traffic lights

\subsection{Camera Component}

\subsubsection{What it does and how}
Explain which are the input of module, output and tasks.
Explain what each task does.
\subsubsection{Complexity}
Explain the complexity of the tasks and their dependencies
\subsubsection{Response time}
Response time analysis and on which device each task runs.
Table or graph about response times.

\subsection{Lidar Segmentation Component}

\subsubsection{What it does and how}
Explain which are the input of module, output and tasks.
Explain what each task does.
\subsubsection{Complexity}
Explain the complexity of the tasks and their dependencies
\subsubsection{Response time}
Response time analysis and on which device each task runs.
Table or graph about response times.

\subsection{Lidar Recognition Component}

\subsubsection{What it does and how}
Explain which are the input of module, output and tasks.
Explain what each task does.
\subsubsection{Complexity}
Explain the complexity of the tasks and their dependencies
\subsubsection{Response time}
Response time analysis and on which device each task runs.
Table or graph about response times.

\subsection{Fusion Component}

\subsubsection{What it does and how}
Explain which are the input of module, output and tasks.
Explain what each task does.
\subsubsection{Complexity}
Explain the complexity of the tasks and their dependencies
\subsubsection{Response time}
Response time analysis and on which device each task runs.
Table or graph about response times.

\subsection{Traffic Light Component}

\subsubsection{What it does and how}
Explain which are the input of module, output and tasks.
Explain what each task does.
\subsubsection{Complexity}
Explain the complexity of the tasks and their dependencies
\subsubsection{Response time}
Response time analysis and on which device each task runs.
Table or graph about response times.

\section{Prediction}

\section{Planning}

\section{Memory Throughput Simulation}
Analyze the impact of accelerating, through a PCI device, the inference of CNN in terms of memory movements from the GPU/CPU to PCI Device.

\section{Simulation Details}
Datasets, gpu, cpu, software used and so on

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} Shih-Chieh Lin, Yunqi Zhang, Chang-Hong Hsu, Matt Skach, Md E. Haque, Lingjia Tang, and Jason Mars, ``The Architectural Implications of Autonomous Driving: Constraints and Acceleration.'' In Proceedings of the Twenty-Third International Conference on Architectural Support for Programming Languages and Operating Systems (ASPLOS '18). ACM, New York, NY, USA, 751-766. DOI: https://doi.org/10.1145/3173162.3173191
%\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2019-04-18 paper/template/conference_041818.tex
Added text to the introduction

@@
 \usepackage{graphicx}
+\usepackage{float}
 \usepackage{textcomp}
 \usepackage{xcolor}
+\usepackage{dblfloatfix}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
     Autonomous driving is a field that gathers many interest from the academics world and from industry leaders.\\
-    The software of an autonomous driving systems (ADS) incorporates the state-of-the-art from many disciplines, such as computer vision, robotics, geolocalization.
+    The software of an autonomous driving systems (ADS) incorporates the state-of-the-art from many disciplines, such as computer vision, robotics, geo-localization.
     Although the high level architecture of an autonomous driving system and the main algorithms used are known, the complete analysis of a real ADS is still difficult, especially for what concerns the modules interdependencies, interactions, either software and hardware, and pre- and post-processing.\\
@@
 
-Response time \cite{b1} is crucial for the predictability and accuracy of the system, especially when multiple sensor and components are present, each of them with a processing routine associated.
-The maximum response time, that has been adopted as standard in the field of autonomous driving, is 100 ms and should ensure a proper and safe reaction to any possible situation.
-Several processing routines use time deltas to perform corrections and projections of input and if those time-deltas are exceeding context-related thresholds then the input is discarded, losing some potential useful information, so limiting the response time will affect also the accuracy of the system.
+Response time \cite{b1} is crucial for the predictability and accuracy of the system, especially when multiple sensors and components are present, each of them with a processing routine associated.
+The maximum response time, which has been adopted as standard in the field of autonomous driving, is 100 ms and should ensure a proper and safe reaction to any possible situation.
+Several processing routines use time deltas to perform corrections and projections of input and if those time-deltas are exceeding context-related thresholds then the input is discarded, losing some potential useful information, thus limiting the response time will affect also the accuracy of the system.
+
+Apollo is a modular data-driven ADS, containing several modules, each of them pursues an high level feature of autonomous driving, such as perception, prediction, planning, control, localization.
+Modules can be treated as black boxes and described in terms of input/output relationships.
+This characterization enables the analysis of modules independently, provided that the inputs fed are feasible.
+Modules are further expressed in terms of set of components, which represent lower level tasks.
+Each component follows the same paradigm of modules, which means interactions within a module are based on input/output relationships through a publisher and subscriber architecture.
+
+Cyber is the Apollo's runtime framework that implements the communication among components.
+The publisher and subscriber communication adopted by Cyber is based on channels and messages.
+Messages are serialized objects, using the Google's Protocol Buffer, which then are broadcast on channel(s).
+Each component can be a reader or writer of multiple channels at the same time.
+
+Apollo supports multiple sensors, different prediction evaluators and several scenario-based planners.
+This rich environment carries out the need of having the right hardware equipment to support each task.
+CPU should be able to sustain many multi-threaded algorithms and provides enough cores to execute several processes concurrently.
+GPU is required for the execution of convolutional neural networks (CNN), vector and matrix operations, which are especially encountered in the perception module.
+
+\begin{figure}[htb]
+
+    \centering
+    \includegraphics[width=0.5\textwidth]{images/apollo_software_architecture.png}
+    \caption{Apollo Software Architecture}
+    \label{}
+\end{figure}
+
+\clearpage
 

### 2019-04-20 modules/perception/camera/lib/traffic_light/detector/detection/detection.cc
Start working on prediction

@@ -234,10 +234,10 @@ bool TrafficLightDetection::Inference(
 
 bool TrafficLightDetection::Detect(const TrafficLightDetectorOptions &options,
                                    CameraFrame *frame) {
-  if (frame->traffic_lights.size() <= 0) {
-    AINFO << "no lights to detect";
-    return true;
-  }
+  //if (frame->traffic_lights.size() <= 0) {
+  //  AINFO << "no lights to detect";
+  //  return true;
+  //}
 
   const auto &data_provider = frame->data_provider;
   auto input_blob = rt_net_->get_blob(net_inputs_[0]);

### 2019-04-20 modules/perception/camera/test/camera_lib_traffic_light_detector_detection_test.cc

@@ -15,6 +15,8 @@
  *****************************************************************************/
 
 #include "modules/perception/camera/lib/traffic_light/detector/detection/detection.h"
+#include "cyber/common/log.h"
+#include "gtest/gtest.h"
 
 namespace apollo {
 namespace perception {

### 2019-04-20 modules/perception/fusion/lib/fusion_system/probabilistic_fusion/probabilistic_fusion.cc

@@ -110,6 +110,10 @@ bool ProbabilisticFusion::Fuse(const FusionOptions& options,
                                std::vector<base::ObjectPtr>* fused_objects) {
   CHECK(fused_objects != nullptr) << "fusion error: fused_objects is nullptr";
 
+  apollo::cyber::Time start, end;
+
+  start = apollo::cyber::Time::Now();
+
   auto* sensor_data_manager = SensorDataManager::Instance();
   // 1. save frame data
   data_mutex_.lock();
@@ -138,10 +142,15 @@ bool ProbabilisticFusion::Fuse(const FusionOptions& options,
     sensor_data_manager->AddSensorMeasurements(sensor_frame);
   }
 
+  end = apollo::cyber::Time::Now();
+
   data_mutex_.unlock();
   if (!is_publish_sensor) {
     return true;
   }
+
+  AINFO << "Measurements Insertion: " << (double)(end - start).ToNanosecond() / 1E6;
+  start = apollo::cyber::Time::Now();
 
   // 2. query related sensor_frames for fusion
   fuse_mutex_.lock();
@@ -150,13 +159,24 @@ bool ProbabilisticFusion::Fuse(const FusionOptions& options,
   sensor_data_manager->GetLatestFrames(fusion_time, &frames);
   AINFO << "Get " << frames.size() << " related frames for fusion";
 
+  end = apollo::cyber::Time::Now();
+  AINFO << "Latest Frames: " << (double)(end - start).ToNanosecond() / 1E6;
+  start = apollo::cyber::Time::Now();
+
   // 3. peform fusion on related frames
   for (size_t i = 0; i < frames.size(); ++i) {
     this->FuseFrame(frames[i]);
   }
 
+  end = apollo::cyber::Time::Now();
+  AINFO << "Fusion Frames: " << (double)(end - start).ToNanosecond() / 1E6;
+  start = apollo::cyber::Time::Now();
+
   // 4. collect fused objects
   this->CollectFusedObjects(fusion_time, fused_objects);
+
+  end = apollo::cyber::Time::Now();
+  AINFO << "Fusion Collection: " << (double)(end - start).ToNanosecond() / 1E6;
 
   fuse_mutex_.unlock();
   return true;

### 2019-04-20 modules/perception/fusion/lib/fusion_system/probabilistic_fusion/probabilistic_fusion.h

@@ -19,6 +19,7 @@
 #include <string>
 #include <vector>
 
+#include "cyber/cyber.h"
 #include "modules/perception/fusion/base/sensor_data_manager.h"
 #include "modules/perception/fusion/lib/interface/base_data_association.h"
 #include "modules/perception/fusion/lib/interface/base_fusion_system.h"

### 2019-04-20 modules/perception/onboard/component/trafficlights_perception_component.cc

@@ -288,7 +288,7 @@ void TrafficLightsPerceptionComponent::OnReceiveImage(
     const std::shared_ptr<apollo::drivers::Image> msg,
     const std::string& camera_name) {
   std::lock_guard<std::mutex> lck(mutex_);
-  double receive_img_timestamp = lib::TimeUtil::GetCurrentTime();
+  //double receive_img_timestamp = lib::TimeUtil::GetCurrentTime();
   double image_msg_ts = msg->measurement_time();
   image_msg_ts += image_timestamp_offset_;
   last_sub_camera_image_ts_[camera_name] = image_msg_ts;
@@ -301,7 +301,17 @@ void TrafficLightsPerceptionComponent::OnReceiveImage(
           << GLOG_TIMESTAMP(cur_time) << "]:cur_latency[" << start_latency
           << "]";
   }
+  PERCEPTION_PERF_BLOCK_START();
+  const std::string perf_indicator = "trafficlights";
 
+  camera::TLPreprocessorOption preprocess_option;
+  preprocess_option.image_borders_size = &image_border_sizes_;
+
+  if (!UpdateCameraSelection(image_msg_ts, preprocess_option, &frame_)) {
+    AWARN << "add_cached_camera_selection failed, ts: "
+          << std::to_string(image_msg_ts);
+  }
+  /*
   const std::string perf_indicator = "trafficlights";
   PERCEPTION_PERF_BLOCK_START();
   if (!CheckCameraImageStatus(image_msg_ts, check_image_status_interval_thresh_,
@@ -349,7 +359,7 @@ void TrafficLightsPerceptionComponent::OnReceiveImage(
     //    SendSimulationMsg();
     return;
   }
-
+  */
   // Fill camera frame
   camera::DataProvider::ImageOptions image_options;
   image_options.target_color = base::Color::RGB;
@@ -358,10 +368,11 @@ void TrafficLightsPerceptionComponent::OnReceiveImage(
       image_height_, image_width_,
       reinterpret_cast<const uint8_t*>(msg->data().data()), msg->encoding());
   frame_.timestamp = image_msg_ts;
-  const auto fill_image_data_time =
-      PERCEPTION_PERF_BLOCK_END_WITH_INDICATOR(perf_indicator, "FillImageData");
+  //const auto fill_image_data_time =
+  //    PERCEPTION_PERF_BLOCK_END_WITH_INDICATOR(perf_indicator, "FillImageData");
 
   // caros monitor -- image system time diff
+  /*
[…]

### 2019-04-20 modules/prediction/common/message_process.cc

@@ -106,25 +106,25 @@ void MessageProcess::OnPerception(
         *ptr_ego_vehicle, ptr_ego_vehicle->timestamp());
     double x = ptr_ego_vehicle->position().x();
     double y = ptr_ego_vehicle->position().y();
-    ADEBUG << "Get ADC position [" << std::fixed << std::setprecision(6) << x
+    AINFO << "Get ADC position [" << std::fixed << std::setprecision(6) << x
            << ", " << std::fixed << std::setprecision(6) << y << "].";
     ptr_ego_trajectory_container->SetPosition({x, y});
   }
   auto end_time2 = std::chrono::system_clock::now();
   std::chrono::duration<double> diff = end_time2 - end_time1;
-  ADEBUG << "Time to insert ADC: " << diff.count() * 1000 << " msec.";
+  AINFO << "Time to insert ADC: " << diff.count() * 1000 << " msec.";
 
   // Insert perception_obstacles
   ptr_obstacles_container->Insert(perception_obstacles);
   auto end_time3 = std::chrono::system_clock::now();
   diff = end_time3 - end_time2;
-  ADEBUG << "Time to insert obstacles: " << diff.count() * 1000 << " msec.";
+  AINFO << "Time to insert obstacles: " << diff.count() * 1000 << " msec.";
 
   // Scenario analysis
   ScenarioManager::Instance()->Run();
   auto end_time4 = std::chrono::system_clock::now();
   diff = end_time4 - end_time3;
-  ADEBUG << "Time for scenario_manager: " << diff.count() * 1000 << " msec.";
+  AINFO << "Time for scenario_manager: " << diff.count() * 1000 << " msec.";
 
   // If in junction, BuildJunctionFeature();
   // If not, BuildLaneGraph().
@@ -136,12 +136,12 @@ void MessageProcess::OnPerception(
   }
   auto end_time5 = std::chrono::system_clock::now();
   diff = end_time5 - end_time4;
-  ADEBUG << "Time to build junction features: " << diff.count() * 1000
+  AINFO << "Time to build junction features: " << diff.count() * 1000
          << " msec.";
   ptr_obstacles_container->BuildLaneGraph();
   auto end_time6 = std::chrono::system_clock::now();
   diff = end_time6 - end_time5;
-  ADEBUG << "Time to build cruise features: " << diff.count() * 1000
+  AINFO << "Time to build cruise features: " << diff.count() * 1000
          << " msec.";
[…]

### 2019-04-20 modules/prediction/prediction_component.cc

@@ -113,11 +113,12 @@ bool PredictionComponent::Proc(
     AERROR << "Prediction: cannot receive any localization message.";
     return false;
   }
+  AINFO << "CIAO";
   auto localization_msg = *ptr_localization_msg;
   MessageProcess::OnLocalization(localization_msg);
   auto end_time2 = std::chrono::system_clock::now();
   std::chrono::duration<double> diff = end_time2 - end_time1;
-  ADEBUG << "Time for updating PoseContainer: " << diff.count() * 1000
+  AINFO << "Time for updating PoseContainer: " << diff.count() * 1000
          << " msec.";
 
   // Read planning info. of last frame and call OnPlanning to update
@@ -130,7 +131,7 @@ bool PredictionComponent::Proc(
   }
   auto end_time3 = std::chrono::system_clock::now();
   diff = end_time3 - end_time2;
-  ADEBUG << "Time for updating ADCTrajectoryContainer: " << diff.count() * 1000
+  AINFO << "Time for updating ADCTrajectoryContainer: " << diff.count() * 1000
          << " msec.";
 
   // Get all perception_obstacles of this frame and call OnPerception to
@@ -140,7 +141,7 @@ bool PredictionComponent::Proc(
   MessageProcess::OnPerception(perception_msg, &prediction_obstacles);
   auto end_time4 = std::chrono::system_clock::now();
   diff = end_time4 - end_time3;
-  ADEBUG << "Time for updating PerceptionContainer: " << diff.count() * 1000
+  AINFO << "Time for updating PerceptionContainer: " << diff.count() * 1000
          << " msec.";
 
   // Postprocess prediction obstacles message

### 2019-04-20 modules/scenario/point_cloud_provider/point_cloud_provider_component.cc

@@ -135,7 +135,7 @@ bool PointCloudProviderComponent::Proc()
             point_xyzit->set_y(buffer[i + 1]);
             point_xyzit->set_z(buffer[i + 2]);
             point_xyzit->set_intensity(uint(buffer[i + 3]));
-            //point_xyzit->set_timestamp(ulong(apollo::cyber::Time::Now().ToSecond()));
+            point_xyzit->set_timestamp(ulong(apollo::cyber::Time::Now().ToNanosecond()));
         }
         //point_clouds.push_back(point_cloud);
         delete[] buffer;
@@ -144,7 +144,7 @@ bool PointCloudProviderComponent::Proc()
     
     for(int i = 0; i < point_cloud->point_size(); i++)
     {
-        point_cloud->mutable_point(i)->set_timestamp(ulong(apollo::cyber::Time::Now().ToSecond()));
+        point_cloud->mutable_point(i)->set_timestamp(ulong(apollo::cyber::Time::Now().ToNanosecond()));
     }
 
     point_cloud->mutable_header()->set_frame_id(FLAGS_velodyne_id);

### 2019-04-21 paper/template/paper.tex
Almost finished the introduction

--- 2019-04-18 paper/template/conference_041818.tex
@@
 \usepackage{graphicx}
-\usepackage{float}
 \usepackage{textcomp}
@@
 \usepackage{dblfloatfix}
+\usepackage{svg}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 
-\title{Complete Workload Analysis of Real Autonomous Driving System: Apollo, Baidu Inc.}
+\title{Workload Analysis of Autonomous Driving System: Apollo, Baidu Inc.}
 
@@
 
-\begin{figure}[htb]
+A schematic overview of the Apollo software architecture is presented in Figure \ref{apollo_software_architecure}.
+Although the communication is data-driven, is reasonable to describe the architecture starting from sensors.
+Apollo supports two Full-HD cameras with two different focal lengths, 6mm and 12mm respectively, which are polled at 20 fps.
+Two types of lidars are used in Apollo: 128L and 16L. The 128L lidar is set to be the master sensor in the architecture.
+GPS and IMU data are provided to the localization module in order to estimate the car's position and pose.
+The perception detects obstacles present in the environment perceived from cameras and lidars and then the prediction module predicts obstacle trajectories using detections, localization estimations and trajectories chosen by the planner.
+Finally, the planning module selects the best trajectory, coherent to the route requested and obstacle trajectories, containing the path and speed profile to adopt.
 
+\begin{figure*}[t]
     \centering
-    \includegraphics[width=0.5\textwidth]{images/apollo_software_architecture.png}
+    \includegraphics[width=\textwidth]{images/apollo_software_architecture.png}
     \caption{Apollo Software Architecture}
-    \label{}
-\end{figure}
-
-\clearpage
-
-Autonomous driving requirements.\\
-Introduction to Apollo: what is it, how is it implemented, data communication.\\
-Modules that are going to be analyzed.\\
-Image of apollo software architecture.\\
+    \label{apollo_software_architecure}
+\end{figure*}
 

### 2019-04-21 paper/template/paper.tex
Finished introduction

@@
 \begin{abstract}
-    Autonomous driving is a field that gathers many interest from the academics world and from industry leaders.\\
+    Autonomous driving is a field that gathers many interest from the academics world and from industry leaders.
     The software of an autonomous driving systems (ADS) incorporates the state-of-the-art from many disciplines, such as computer vision, robotics, geo-localization.
-    Although the high level architecture of an autonomous driving system and the main algorithms used are known, the complete analysis of a real ADS is still difficult, especially for what concerns the modules interdependencies, interactions, either software and hardware, and pre- and post-processing.\\
-    In this paper, we want to extract those point of views and quantify them according different architectural aspects: response times, memory movements, complexity and CPU-GPU relationship.\\
+    Although the high level architecture of an autonomous driving system and the main algorithms used are known, the complete analysis of a real ADS is still difficult, especially for what concerns the modules interdependencies, interactions, either software and hardware, and pre- and post-processing.
+    In this paper, we want to extract those point of views and quantify them according different architectural aspects: response times, memory movements, computational complexity and CPU-GPU relationship.
     The analysis is based on the open-source Apollo ADS developed by Baidu and is focused on the most important modules: perception, prediction and planning.
@@
 Finally, the planning module selects the best trajectory, coherent to the route requested and obstacle trajectories, containing the path and speed profile to adopt.
+Many modules rely on HDMap to get an enriched understanding of the surrounding environment, being able to query road signs, junctions, lanes and many more.
 
+In the next sections, we will describe the perception, prediction and planning modules.
+The description will be composed by an high level overview of the module and the analysis of each component within the module.
+The analysis is focused on response times, computational complexity, data dependencies, CPU-GPU relationship and memory movements.
+In the last section, we will detail the simulation environment, settings and datasets used in this work.
 \begin{figure*}[t]

### 2019-04-21 paper/template/paper.tex
Started perception

@@
 \usepackage{dblfloatfix}
-\usepackage{svg}
+\usepackage{inputenc}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 \begin{document}
+
+%\pagenumbering{arabic}
+%\thispagestyle{plain}
+%\pagestyle{plain}
 
@@
 In the last section, we will detail the simulation environment, settings and datasets used in this work.
+
 \begin{figure*}[t]
@@
 
+\begin{figure*}[b!]
+    \centering
+    \includegraphics[width=\textwidth]{images/perception_software_architecture.png}
+    \caption{Perception Software Architecture}
+    \label{perception_software_architecture}
+\end{figure*}
+
 \section{Perception}
+The perception module perceives the environment, through the data coming from cameras and lidars, by detecting obstacles.
+In the Figure \ref{perception_software_architecture} is presented the internal representation of the perception modules, highlighting the module's components and flow.
+Due to the different nature of the inputs, camera frames and cloud points require different detection algorithm, pre- and post-processing.
+The Fusion Camera Detection is a unique component shared from both 6mm and 12mm camera frames.
+
 Perception diagram.

### 2019-04-22 paper/template/paper.tex
Fusion component

@@
     \centering
-    \includegraphics[width=\textwidth]{images/apollo_software_architecture.png}
+    \includegraphics[height=3.7cm]{images/apollo_software_architecture.png}
     \caption{Apollo Software Architecture}
@@
     \centering
-    \includegraphics[width=\textwidth]{images/perception_software_architecture.png}
+    \includegraphics[height=3.7cm]{images/perception_software_architecture.png}
     \caption{Perception Software Architecture}
@@
 Due to the different nature of the inputs, camera frames and cloud points require different detection algorithm, pre- and post-processing.
-The Fusion Camera Detection is a unique component shared from both 6mm and 12mm camera frames.
+The Fusion Camera Detection is a unique component shared from both 6mm and 12mm camera frames and processes them using first-in, first-served policy through an Obstacle Camera Pipeline.
+The Lidar Segmentation is bounded to a specific Lidar because different lidars have different parameters that affect the segmentation.
+Thus, cloud points are published into distinct Cyber's channels according to the lidars and the segmentation components are driven by those channels concurrently.
+The ouput of lidar segmentation doens't depends anymore on the lidar of origin, the recognition component indeed is unique and shared.
+Intermediate detections converge on the Fusion component, which will provide coherent and combined detections among sensors, publishing them as the output of the whole module.
 
-Perception diagram.
-General description: what it does, sensors descriptions, output and general overview.
+\subsection{Fusion Camera Detection}
 
-For each component: camera, lidar segmentation, lidar recognition, fusion component and traffic lights
+The Fusion Camera Detection applies a sequence of tasks, called Obstacle Camera Pipeline, to camera frames.
+The pipeline is composed by lanes detection and post-processing, obstacles tracking and obstacles detection and post-processing.
+The pipeline is not applied equally to each frame; lanes detection and post-processing are only applied to camera frames coming from the 6mm camera, due to the wider perspective.
 
-\subsection{Camera Component}
+Lanes detection is performed using SCNN \cite{b2}, spatial convolutional neural network, which exploits spatial relationship among pixels in order to identify straight shaped obstacles, such as lanes.
+To fit the SCNN input size, the camera frame is resized from 1920x1080 to 640x480 and then forwarded through the network.
+The network detects at most 13 lanes, the output indeed can be interpreted as 13 frames of size 640x480 each of which highlights a lane if present. 
+This sparse output is then fused to a single 640x480 frame, in which different lanes are highlighted by different identifiers.
 
-\subsubsection{What it does and how}
-Explain which are the input of module, output and tasks.
-Explain what each task does.
-\subsubsection{Complexity}
+Lanes post-processing needs to be applied because lanes' representation is not yet meaningful for the subsequent modules in the ADS.
+The lanes found so far belong to the camera plane and need to be projected onto car plane and ground plane.
+For each lane, the third-order polynomial coefficients are estimated from the ground plane projection using the Ransac-Fitting algorithm.
+Finally a further projection is executed, converting the lane points from the two bi-dimensional planes onto the three-dimensional plane, represented in world coordinates.
+
+Obstacles are detected using 'YoloNET' convolutional neural network which is able to identify 2D bounding boxes of obstacles and their classes.
+Likewise the lanes detection, the camera frame is resized to fit the size of the neural network. After the inference, the 2D bounding boxes are projected onto the 3D by the obstacle post-processor.
+
+The obstacles tracker adapts the detections of the previous iteration to the current one by estimating the new bouding boxes position according an Adaptive Kalman Filter, car pose and time-deltas.
+Afterwards, the obstacles tracker matches new obstacles detected to the previous ones, generates hypothesys and deletes the duplicates.
+Finally, the obstacles detected are propagated towards the Fusion component.
+
+\subsubsection*{Complexity}
 Explain the complexity of the tasks and their dependencies
-\subsubsection{Response time}
+\subsubsection*{Response time}
 Response time analysis and on which device each task runs.
@@
 \subsection{Fusion Component}
-
-\subsubsection{What it does and how}
-Explain which are the input of module, output and tasks.
-Explain what each task does.
-\subsubsection{Complexity}
-Explain the complexity of the tasks and their dependencies
-\subsubsection{Response time}
-Response time analysis and on which device each task runs.
-Table or graph about response times.
-
-\subsection{Traffic Light Component}
 
@@
 \begin{thebibliography}{00}
-\bibitem{b1} Shih-Chieh Lin, Yunqi Zhang, Chang-Hong Hsu, Matt Skach, Md E.
-Haque, Lingjia Tang, and Jason Mars, ``The Architectural Implications of Autonomous Driving: Constraints and Acceleration.'' In Proceedings of the Twenty-Third International Conference on Architectural Support for Programming Languages and Operating Systems (ASPLOS '18).
-ACM, New York, NY, USA, 751-766.
-DOI: https://doi.org/10.1145/3173162.3173191
+\bibitem{b1} Lin, S.
+C., Zhang, Y., Hsu, C.
+H., Skach, M., Haque, M.
+E., Tang, L., \& Mars, J.
+(2018, March).
+The architectural implications of autonomous driving: Constraints and acceleration.
+In ACM SIGPLAN Notices (Vol.
+53, No.
+2, pp.
+751-766).
+ACM.
 %\bibitem{b1} G.
@@
 529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
+\bibitem{b2} Pan, X., Shi, J., Luo, P., Wang, X., \& Tang, X. (2018, April). Spatial as deep: Spatial cnn for traffic scene understanding. In Thirty-Second AAAI Conference on Artificial Intelligence.
 \bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.

### 2019-04-23 paper/template/paper.tex
Finished camera

@@
 \usepackage{dblfloatfix}
-\usepackage{inputenc}
+\usepackage{subcaption}
+\usepackage{adjustbox}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
     \centering
-    \includegraphics[height=3.7cm]{images/apollo_software_architecture.png}
+    \includegraphics[height=2.5cm]{images/apollo_software_architecture.png}
     \caption{Apollo Software Architecture}
@@
     \centering
-    \includegraphics[height=3.7cm]{images/perception_software_architecture.png}
+    \begin{subfigure}{\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth, height=2.5cm]{images/perception_software_architecture.png}
         \caption{Perception Software Architecture}
         \label{perception_software_architecture}
+    \end{subfigure}
+    \begin{subfigure}{\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth,height=2.5cm]{images/obstacle_camera_pipeline.png}
+        \caption{Obstacle Camera Pipeline}
+        \label{obstacle_camera_pipeline}
+    \end{subfigure}
+    \caption{}
 \end{figure*}
+
+%\begin{figure}[b!]
+%    \centering
+%    \includegraphics[height=2.5cm]{images/perception_software_architecture.png}
+%    \caption{Perception Software Architecture}
+%    \label{perception_software_architecture}
+%\end{figure}
+%
+%\begin{figure}[b!]
+%    \centering
+%    \includegraphics[height=2.5cm]{images/obstacle_camera_pipeline.png}
+%    \caption{Obstacle Camera Pipeline}
+%    \label{obstacle_camera_pipeline}
+%\end{figure}
 
@@
 
-The Fusion Camera Detection applies a sequence of tasks, called Obstacle Camera Pipeline, to camera frames.
+The Fusion Camera Detection applies a sequence of tasks, called Obstacle Camera Pipeline to camera frames, displayed in Figure \ref{perception_software_architecture}.
 The pipeline is composed by lanes detection and post-processing, obstacles tracking and obstacles detection and post-processing.
@@
 \subsubsection*{Complexity}
-Explain the complexity of the tasks and their dependencies
+
+The computational complexity of the whole pipeline is dominated by CNN inferences.
+Lanes detection, in addition, depends on image resizing and the fusion of detected lanes into one frame.
+Lanes post-processing performs several operations on lane points of each lanes detected and the iterative RANSAC algorithm to find the polynomial coefficients.
+The tracker prediction relies only to the past obstacles detected and the update of the Adaptive Kalman Filter.
+The obstacles detection, similarly to the lane detection, resizes the image and performs some refinements on the obstacles candidates to refine their bounding boxes.
+The obstacles post-processing and tracking association involve the comparison between past obstacles and current obstacles.
+
+\begin{table}[htbp]
+    \begin{center}
+    \begin{adjustbox}{max width=\columnwidth}
+        \setlength{\tabcolsep}{0.5em}
+        \renewcommand{\arraystretch}{1.2}
+        \begin{tabular}{|p{3cm}|p{6cm}|}
+            \hline
+            \textbf{Task} & \textbf{Complexity} \\
+            \hline
+            Lanes Detection & CNN inference, image resizing and single lanes frame\\
+            \hline
+            Lanes Post-processing & RANSAC algorithm, lane points x lanes detected \\
+            \hline
+            Tracker Prediction & Past obstacles detected\\
+            \hline
+            Obstacles Detection & CNN inference, image resizing, obstacles candidates, obstacles detected\\
+            \hline
+            Obstacles Post-processing & Obstacles detected\\
+            \hline
+            Tracker Association & Obstacles detected x past obstacles\\
+            \hline
+            \end{tabular}    
+    \end{adjustbox}
+    \label{fusion_detection_component_complexity_table}
+    \end{center}
+    \caption{Fusion Camera Detection Complexity}
+\end{table}
+
 \subsubsection*{Response time}
-Response time analysis and on which device each task runs.
-Table or graph about response times.
+
+The average response time of the component in our simulation is 49.76 ms and the 95.86\% of time is spent on CNN inferences.
+This dominance of CNN inferences lead to make the computation independent from the number of obstacles detected, even if the pre- and post-processing operations are needed to generate a correct detection.
+This component heavily relies on GPU for the CNN inferences, image resizing, the extraction of the obstacles bounding boxes from the YoloNet output and the similarities between obstacles and frames in the tracking phase.
+
+\begin{table}[htbp]
+    \begin{center}
+    \begin{adjustbox}{max width=\columnwidth}
+        \setlength{\tabcolsep}{0.5em}
+        \renewcommand{\arraystretch}{1.2}
+        \begin{tabular}{|l|r|r|}
+            \hline
+            \textbf{Task}&\multicolumn{2}{|c|}{\textbf{Response Time}} \\
+            \cline{2-3} 
+            & \textbf{\textit{ms}}& \textbf{\textit{\%}}\\
+            \hline
+            Lanes Detection & 38.14 & 76.65\\
+            \hline
+            Lanes Post-processing & 0.72 & 1.45 \\
+            \hline
+            Tracker Prediction & 0.01 & 0.02\\
+            \hline
+            Obstacles Detection & 9.56 & 19.21\\
+            \hline
+            Obstacles Post-processing & 0.6 & 1.2\\
+            \hline
+            Tracker Association & 0.73 & 1.47\\
+            \hline
+            \end{tabular}    
+    \end{adjustbox}
+    \label{fusion_detection_component_response_time_table}
+    \end{center}
+    \caption{Fusion Camera Detection Response Time}
+\end{table}
 
